Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-18 writeup/gz_hubble_data.tex
GEMS/GZH comparison, part 1

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{deluxetable}
\usepackage{url}
\bibliographystyle{mn2e}

\input{gzh_macros.tex}

@@

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item GEMS morphologies \citep{hau07}
    \item AEGIS morphologies \citep{lot08}
    \item GOODS N/S morphologies \citep{bun05}
\end{itemize}

>>>>

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{deluxetable}
\usepackage{url}
\usepackage[normalem]{ulem}
\bibliographystyle{mn2e}

\input{macros.tex}

@@

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item \sout{GEMS morphologies} \citep{hau07}
    \item AEGIS morphologies \citep{lot08}
    \item GOODS N/S morphologies \citep{bun05}
\end{itemize}

Morphologies for galaxies in GEMS imaging have been measured by \citet{hau07}, who perform a careful comparison of single-component \sersic{} fits to the F850LP imaging using both the \galfit{} and \gimtwod{} codes. We compare the GZH morphological vote fractions to the \galfit{} parameters, which are evaluated by \citet{hau07} as more reliable due to \galfit's ability to fit multiple galaxies and handle crowded fields.

A single \sersic{} fit is often a poor fit to the light profile of a resolved galaxy, since large numbers of classical spirals have both a de~Vaucouleurs bulge at the center and an exponential disc at larger radii. If a single parameter is used, however, a common division in the literature is to split on the \sersic~index $n$ into disc-dominated galaxies ($n<2.5$) and bulge-dominated galaxies ($n>2.5$), where $n$ is the exponent in the radial surface brightness profile such that $\Sigma(r)=\Sigma_e \exp{\left(-\kappa[(r/r_e)^{1/n} - 1]\right)}$.

A 1\arcsec~positional match for the GEMS galaxies in Table~9 in \citet{hau07} to the GZH sample gives 8,846~galaxies found in both samples. We analyze galaxies for which the \galfit{} parameters are flagged as being constrained within plausible physical limits, indicating a moderately robust fit. There is a strong correlation between $n$ and \pbest; the average value for disk-dominated galaxies ($n<2.5$) is $\langle$\pbest$\rangle=0.44\pm0.26$, compared to $\langle$\pbest$\rangle=0.30\pm0.25$ for bulge-dominated galaxies ($n>2.5$). The correlation is stronger for bulge-dominated galaxies; for $n>2.5$, most galaxies have \pbest$<0.2$. In contrast, while $n<2.5$ do have higher \pbest~values, the spread is larger and there are significant numbers of galaxies even at the highest \pbest{} values.

Inverting the comparison, we split the GZH galaxies into three samples: ``clean'' disks (\pbest$\ge0.8$), ``clean'' ellipticals (\pbest$\le0.2$), and ``intermediate'' ($0.2<$\pbest$<0.8$) galaxies \citep[eg,][]{sch14}. Splitting by $n<2.5/n>2.5$, clean disks are $85\%/17\%$, intermediates $84\%/16\%$, and clean ellipticals $59\%/41\%$. There is a strong dependence for these ratios on the brightness of the galaxy, which affects both automatic fits and visual accuracy. Limiting the sample to galaxies with $m_{850LP}<21$ gives fractions of: clean disks are $77\%/23\%$, intermediates $52\%/48\%$, and clean ellipticals $38\%/62\%$. While the clean disk fraction is largely unchanged, intermediates are more evenly balanced and there is a larger population of smooth galaxies with high $n$, as expected.

Clumpy galaxies in GZH have $n$ and $R_e$ \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/gems_clumpy.png}
\caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH. Red and blue points indicate galaxies split by their \sersic~index into disk- and bulge-dominated galaxies. Galaxies identified as ``clumpy'' in GZH are labeled in green.}
\label{fig:clumpy_gems}
\end{center}
\end{figure}
